### 2012-11-28 inst/examples/reed-example.Rmd
Example direct method (using package functions from this repo) with preset hyperparameters.

```{r graphing-options, include=FALSE}
require(pdgControl)
require(nonparametricbayes)
require(ggplot2)
library(kernlab)
opts_knit$set(upload.fun = socialR::notebook.url)
opts_chunk$set(dev.args=list(bg="transparent"), comment=NA, tidy=FALSE)
theme_set(theme_bw())
theme_update(panel.background = element_rect(fill = "transparent",colour = NA),
             plot.background = element_rect(fill = "transparent",colour = NA))
```

@@

```{r}
gp <- gp_fit(obs, X, c(sigma_n=.2, l=10))
plot.gpfit(gp, true)
```

@@

```{r}
matrices_gp <- gp_transition_matrix(gp)
matrices_true <- f_transition_matrix(f, p, x_grid)
opt_true <- find_dp_optim(matrices_true, x_grid, h_grid, 20, 0, profit, delta=.01)
opt_gp <- find_dp_optim(matrices_gp, x_grid, h_grid, 20, 0, profit, delta=.01)
```

```{r policy_plot}
require(reshape2)
policies <- melt(data.frame(stock=x_grid, GP = x_grid[opt_gp$D[,1]], Exact = x_grid[opt_true$D[,1]]), id="stock")
policy_plot <- ggplot(policies, aes(stock, stock - value, color=variable)) +
  geom_point() + xlab("stock size") + ylab("escapement") 
policy_plot
```

>>>>

```{r graphing-options, include=FALSE}
require(pdgControl)
require(nonparametricbayes)
require(reshape2)
require(ggplot2)
library(kernlab)
opts_knit$set(upload.fun = socialR::notebook.url)
opts_chunk$set(dev.args=list(bg="transparent"), comment=NA, tidy=FALSE)
theme_set(theme_bw())
theme_update(panel.background = element_rect(fill = "transparent",colour = NA),
             plot.background = element_rect(fill = "transparent",colour = NA))
```

@@

```{r}
gp <- gp_fit(obs, X, c(sigma_n=.1, l=8))
plot.gpfit(gp, true)
```

@@

```{r}
h_grid <- x_grid
matrices_gp <- gp_transition_matrix(gp)
matrices_true <- f_transition_matrix(f, p, x_grid, h_grid)
opt_true <- find_dp_optim(matrices_true, x_grid, h_grid, 20, 0, profit, delta=.01)
opt_gp <- find_dp_optim(matrices_gp, x_grid, h_grid, 20, 0, profit, delta=.01)
```

```{r policy_plot}
policies <- melt(data.frame(stock=x_grid, GP = x_grid[opt_gp$D[,1]], Exact = x_grid[opt_true$D[,1]]), id="stock")
policy_plot <- ggplot(policies, aes(stock, stock - value, color=variable)) +
  geom_point() + xlab("stock size") + ylab("escapement") 
policy_plot
```
